---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{CVPASapp}`

## Installation

The CVPAS app code is housed within an R package. To run the app locally you will neeed to navigate to the root directory 'CVPASapp' then run the following code to:

minor

```{r eval=TRUE,comment=""}
fs::dir_tree(type="directory")
```

## Development notes

### good prefix defs
"draw" means create a user interface
"get" means to look up content to place somewhere
"utils" means general tool used in many places

### good suffix defs
"txt" mean character string
"ui" means R shiny UI code (tagList())

### /R basic package functions
data.R

### /R basic shiny functions
app_server.R
app_ui.R
run_app.R

### /R golem and extra shiny package functions
data.R

## Alterations
- maybe "ggplot" should be a suffix and not a prefix
- choose either "details" or "deets" probably should do details
- get rid of "extract" prefix because and use "get" or "calc"
- These utils functions are weird: "utils_plotting.R","utils_prep_datasets.R"


```{r,
# library(data.tree)

# acme <- Node$new("Acme Inc.")
#   accounting <- acme$AddChild("Accounting")
#     software <- accounting$AddChild("New Software")
#     standards <- accounting$AddChild("New Accounting Standards")
#   research <- acme$AddChild("Research")
#     newProductLine <- research$AddChild("New Product Line")
#     newLabs <- research$AddChild("New Labs")
#   it <- acme$AddChild("IT")
#     outsource <- it$AddChild("Outsource")
#     agile <- it$AddChild("Go agile")
#     goToR <- it$AddChild("Switch to R")

```


## Running the app

```{r, eval = FALSE}

# loads all of the required functions into your environment
# devtools::load_all("CVPASapp")

# launches the application
# CVPASapp::run_app()
```

This README has been compiled on the

```{r}
Sys.time()
```

```{r echo = FALSE}
# unloadNamespace("CVPASapp")
```
